Kronos \& Krios: Evidence for accretion of a massive, rocky planetary system in a sun-like pair

### 2017-06-09 paper/ms.tex
space in todo
oops, explain histogram too

\newcommand{\todo}[1]{{\color{blue}TODO:#1}}

@@

%TODO: APW what is the histogram of?
%TODO: plot styles...
\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{orbits.pdf}
  \end{center}
  \caption{Galactic orbits computed for \sunanalog\ (black) and the Sun (grey).
    For \sunanalog, the initial conditions are set to the median of the
    posterior sample over the phase-space coordinates.
    The orbits are computed by integrating backwards from the present-day
    positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
    integration scheme implemented in \project{Gala} (\citealt{gala}).
  }
  \label{fig:orbit}
\end{figure}

>>>>

\newcommand{\todo}[1]{{\color{blue}TODO: #1}}

@@

%TODO: plot styles...
\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{orbits.pdf}
  \end{center}
  \caption{Left panel: Galactic orbits computed for \sunanalog\ (black) and the
    Sun (grey).
    For \sunanalog, the initial conditions are set to the median of the
    posterior samples over the phase-space coordinates.
    The orbits are computed by integrating backwards from the present-day
    positions for $2.5$~Gyr with a time step of $0.5$~Myr using the Leapfrog
    integration scheme implemented in \project{Gala} (\citealt{gala}).
    Right panel: distribution of maximum $z$-heights for orbits computed from
    all posterior samples.
  }
  \label{fig:orbit}
\end{figure}
